---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BDBB

<!-- badges: start -->
<!-- badges: end -->

The goal of BDBB is to mine the co-methylation patterns hidden in the MeRIP-Seq data, which require the IP and input data matrices to be first approximated into methylation levels. It can also be used for pattern mining of data that follows a beta-mixture distribution.If you use BDBB for other types of data mining, the input data must be numeric matrices. 

## Installation

You can install the development version of BDBB like so:

``` r
library(usethis)
library(devtools)
install_github("licong0109/BDBB")
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(BDBB)
## basic example code
number_bicluster <- 6
bic_row_labels <- c(rep(0,dim(mixture)[1]))

simulate_multiple_GSB_object <- multiple_GSB(a = mixture,iteration = 2000,burn_in = 500,bic_row_labels = bic_row_labels,number_bicluster = number_bicluster)
```
